|

### 2021-03-17 documentation/readme.Rmd
Make image a little taller
Remove bold font face

ggsave(
  filename = "timeplot_gh.png",
  plot = timeplot,
  path = here("documentation", "_assets"),
  width = 3.5,
  height = 2,
  units = "in",
  dpi = 320
)

@@

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party** in Britain. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** and **the `r txt_dta$party[3]` in third place**.

>>>>

ggsave(
  filename = "timeplot_gh.png",
  plot = timeplot,
  path = here("documentation", "_assets"),
  width = 3.5,
  height = 2.2,
  units = "in",
  dpi = 320
)

@@

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain. They hold a lead over the `r txt_dta$party[2]` of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. This puts the `r txt_dta$party[2]` in second place and the `r txt_dta$party[3]` in third place.
